%-------------------------

% Resume in Latex

% Author : Abhishek Niranjan

% Shamelessly copied from https://github.com/sb2nov/resume

%------------------------



\documentclass[letterpaper,11pt]{article}



\usepackage{latexsym}

\usepackage[empty]{fullpage}

\usepackage{titlesec}

\usepackage{marvosym}

\usepackage[usenames,dvipsnames]{color}

\usepackage{verbatim}

\usepackage{enumitem}

\usepackage[hidelinks]{hyperref}

\usepackage{fancyhdr}

\usepackage[english]{babel}



\pagestyle{fancy}

\fancyhf{} % clear all header and footer fields

\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}

\renewcommand{\footrulewidth}{0pt}



% Adjust margins

\addtolength{\oddsidemargin}{-0.5in}

\addtolength{\evensidemargin}{-0.5in}

\addtolength{\textwidth}{1in}

\addtolength{\topmargin}{-0.7in}

\addtolength{\textheight}{1.0in}



\urlstyle{same}



\raggedbottom

\raggedright

\setlength{\tabcolsep}{0in}



% Sections formatting

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]



%-------------------------

% Custom commands

\newcommand{\resumeItem}[2]{
  %\setlength{\itemindent}{-2.5ex}
  \item\small{
    \textbf{#1}{: #2 \vspace{-3pt}}
  }
}

\newcommand{\resumeItemx}[2]{
  %\setlength{\itemindent}{-2.5ex}
  \item\small{
    \textbf{#1}{#2 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingSingle}[2]{
  \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}



\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}
\newcommand{\resumeSubItemx}[2]{\resumeItemx{#1}{#2}\vspace{-5pt}}



\renewcommand{\labelitemii}{$\circ$}



\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-16pt}}

\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-4pt}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-9pt}}



%-------------------------------------------

%-------------------------------------------

%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%





\begin{document}



%----------HEADING-----------------

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://abhishek-niranjan.github.io/}{\Large Abhishek Niranjan}} & Email : \href{mailto:abhishek.niranjan.iitkgp@gmail.com}{abhishek.niranjan.iitkgp@gmail.com}\\
  \href{http://github.com/abhishek-niranjan/}{http://github.com/abhishek-niranjan} & Mobile : (+91)-8513902048\\
\end{tabular*}
\vspace{-2ex}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology(IIT)}{Kharagpur, India}
      {Bachelor + Master of Technology in Computer Science; }{July 2013 -- July 2018}
      \vspace{-1.2ex}
%     \resumeSubheading
%       {Kendriya Vidyalaya}{Jodhpur, India}
%       {AISSCE (Grade XII);  Percentage: 93.6\%}{Apr 2011 -- Mar 2012}
   \resumeSubHeadingListEnd





%-----------EXPERIENCE-----------------

\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Observe.ai}{Bangalore, India}
      {Machine Learning Engineer}{Dec 2020 - Present}
      \resumeItemListStart
      \resumeItemx{}
            {Observe provides ML driven services which include analyzing interactions, evaluating performance, and coaching to the contact center workforce.}
      \resumeItemx{}
            {Actively involved in ML platform monitoring exercises; Built a continuous evaluation framework using Apache Airflow to consistently track ML models' accuracy which are deployed in production; Maintainer of New Relic Dashboards of multiple ML services in production.}
      \resumeItemx{}
            {Owner of micro-service which serves as the bridge between the backend team and ML team. The micro-service works as the routing engine to access other REST and queue based ML micro-services.}
      \resumeItemx{}
            {Developed an optimized speech based ML model to filter agent-customer call interactions on the basis of fast speaking rate, articulation issue, and tone. The algorithm resulted in a F1 score of \textit{75\%}. Took charge of designing, implementing and load testing of the micro-service which got deployed in production. }
        \resumeItemx{}
            {Co-developed smart micro-service for resilient on-premise ASR system, in which consumers make dynamic decisions on whether to pick/consume an audio-transcription request based on the resources available at any instant.}
        \resumeItemx{}
            {Introduced the usage of LLD documentation (UML class and sequence diagrams) in the SSDLC process for structured discussions and streamlined knowledge transfer.}
        \resumeItemx{}
            {Currently working on deploying of ESPNET's implementation of streaming transformer ASR system on AWS Sagemaker.  }
        
      \resumeItemListEnd
      \resumeSubheadingSingle{Technologies: REST Framework (Falcon, Gunicorn), Docker, AWS ECS, AWS SQS, AWS Sagemaker, Apache Airflow}{}
      \vspace{-4.5mm}
    \resumeSubheading
      {Samsung Research Institute}{Bangalore, India}
      {Lead Engineer}{Mar 2020 - Dec 2020}
      \resumeItemListStart
      \resumeItem{Whisper Speech Recognition}
            {Bixby is a voice assistant indigenous to Samsung smart devices. As a part of
            Automated Speech Recognition(ASR) team, built a speech-to-whisper conversion system using CycelGAN to generate synthetic whisper signals to augment training data. Research paper accepted in INTERSPEECH 2020.}
      \resumeItem{Speech-to-Speech Translation}
            {Worked on speech translation problem involving conversion of Korean audio signal features to English audio signal features. Using Transformer model as the fundamental sequence-to-sequence architecture with addition of auxiliary decoders to train on parallel tri-phone aligned data.}
      \resumeItemListEnd
    \resumeSubheadingSingle{Senior Software Engineer}{Jun 2018 - Mar 2020}
      \resumeItemListStart
      \resumeItem{Grapheme-to-Phoneme (G2P)}
          {Built and deployed Copy-Augmented Encoder-Decoder Bi-LSTM based architecture to achieve state-of-the-art results on G2P conversion problem. Paper was published in ASRU 2019.}
      \resumeItem{Grammatical Error Correction(GEC)}
           {Developed and deployed a sequence-to-sequence model for Bixby's inverse text normalization (ITN) module. Modified Transformer architecture to handle attention from multi Encoders in an hierarchical fashion for on-device processing in smartphones. }
      \resumeItemListEnd
      \resumeSubheadingSingle{Technologies: TensorFlow, PyTorch, Keras, Shell Scripting}{}
      \vspace{-4.5mm}
    \resumeSubheading
      {Amplus Solar}{Gurgaon, India}
      {Data Science Intern}{May 2017 - July 2017}
      \resumeItemListStart
        \resumeItem{Soiling Rate}
          {Photovoltaic plants experience soiling phenomena which affects the power generation. Developed an algorithm to compute the soiling rate from limited data to devise a \textit{cost-optimized} cleaning schedule of PV plants.}
          \resumeItem{Power-Generation Forecasts}
          {Engineered a forecasting module to predict hourly active power generation by a PV plant 
          using \textit{gradient boosted trees}. achieving a correlation of 0.97; Augmented the feature set by utilizing OpenWeatherMap API.}
        \resumeItem{Power-BI Reports}
          {Automated the generation of daily visualization reports of Solar Plants portfolio in \textit{Power BI} by connecting MySQL server hosted on AWS EC2 instance. Built a GUI application using \textit{PyQt}4 to facilitate the data downloading from multiple dashboards.}
      \resumeItemListEnd
      \resumeSubheadingSingle{Technologies: NumPy, Pandas, Scikit-Learn, PyQt}{}
      \vspace{-4.5mm}
    \resumeSubheading
      {Bidgely Technologies}{Bangalore, India}
      {Data Science Intern}{May 2016 - July 2016}
      \resumeItemListStart
        \resumeItem{Vacation Detection}
          {Bidgely's energy disaggregation technology helps consumers and utilities to adopt eco and pocket friendly consumption. Devised a sliding window algorithm to predict the vacation instances of the residents in \textit{MATLAB with precision \textgreater95\% and recall \textgreater70\%,} which got incorporated into production}
        \resumeItem{Refrigeration Consumption}
          {Worked on the energy disaggregation module to compute refrigerator consumption from low resolution energy data, which was pushed to disaggregation pipeline.}
      \resumeItemListEnd
      \resumeSubheadingSingle{Technologies: MATLAB}{}
      \vspace{-4mm}
    \resumeSubheading
      {Outsy Inc.}{Mumbai, India}
      {Application Developer Intern}{May 2015 - July 2015}
      \resumeItemListStart
        \resumeItem{Information Retrieval}
          {Outsy is a lifestyle and event recommendations android application. Extracted artists' names from 15,000 Facebook textual posts using \textit{Stanford POSTagger} after NLTK assisted pre-processing; Generated artists' profile database using \textit{Wikipedia API, Youtube API, and SoundCloud API.} }
      \resumeItemListEnd
      \resumeSubheadingSingle{Technologies: Python, Django, NLTK, Graph API}{}
  \resumeSubHeadingListEnd



%--------SKILLS------------

% \section{Skills}
%  \resumeSubHeadingListStart
%     \resumeSubItem{Languages}{Python, C++, SQL}
%     \resumeSubItem{Frameworks \& Libraries}{TensorFlow, PyTorch, Keras, Scikit-learn, NumPy, pandas}
%     \resumeSubItem{Softwares \& Tools}{MATLAB, Tableau, Power-BI,  Google Cloud Platform, AWS, Git}
%     \resumeSubItem{Documentation}{\LaTeX}
%  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{1mm}
\section{Projects}
  \resumeSubHeadingListStart
    % \resumeSubItem{Scientific Document Clustering Based on Key-phrases}
    %   {Focused on studying how the popularity of different tasks and techniques related to NLP Research emerges/varies with time as a part of Master's Thesis.}
    \resumeSubItem{Sign Language Translation}
      {Translation of American sign language gestures to text using flex sensing gloves.}
    \resumeSubItem{Data Extractor from 2D Plots}
      {A graph extractor that detects plots in any PDF and digitizes the graphs.}
    \resumeSubItem{Optimal Bidding}
      {Cost optimization algorithm employing solar power prediction to manage a gated community's electricity requirements; Our algorithm secured 1\textsuperscript{st} place in the Inter-IIT 2018 data science competition.}
  \resumeSubHeadingListEnd


\vspace{1mm}
%-----------PUBLICATIONS-----------------
\section{Publications}
  \resumeSubHeadingListStart
    \resumeSubItemx{}{G P R Reddy, Gowtham P V, \textbf{A Niranjan}, K Saranu, R Sarma, M A B Shaik, P Paramasiyam. \textit{Whisper augmented speech recognition system using CycleGAN as speech to whisper domain transfer}. INTERSPEECH 2020}
    \resumeSubItemx{}{\textbf{A Niranjan}, M A B Shaik. \textit{Improving grapheme-to-phoneme conversion by investigating copying mechanism in recurrent architectures}. ASRU 2019}
    \resumeSubItemx{}{\href{https://ieeexplore.ieee.org/document/8614746}{A Mullick, A Bhandari, \textbf{A Niranjan}, N Sekhar, S Garg,  R Bubna, M Roy \textit{Drift in Online Social Media} IEMCON 2018}}
    \resumeSubItemx{}{\href{https://ieeexplore.ieee.org/document/7991589}{Mayank Singh, \textbf{A Niranjan}, D Gupta, N A Bakshi, A Mukherjee, P Goyal. \textit{Citation sentence reuse behavior of scientists: A case study on massive bibliographic text dataset of computer science.} JCDL 2017}}
  \resumeSubHeadingListEnd








%-------------------------------------------

\end{document}